Dynamic Transition Analysis with TIMES

### 2020-11-26 doc/2020-03-paper/methods.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

\section{Methodology} \label{method}
% what is TIMES
\subsection{TIMES Model Description}
\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimization problem that is subject to a primary objective function and additional constraints. The generation, refinement, supply, storage, and trade of energy commodities across multiple sectors and multiple regions are modeled using a wide variety of in-built commodity and process types. Emissions can be associated with energy commodities or processes as an emission coefficient per unit commodity produced or consumed.

@@

While electricity demand in the near future is expected to grow \cite{noauthor_electricity_2019}, long term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population. However, precisely quantifying this rate of decrease is challenging as there is potential for increased electrification of  transportation and industrial sectors. Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification driving increasing demand, but the demand eventually plateaus due to the aforementioned expected demographic changes. The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}. Long term impacts of factors such as the retirement of the existing nuclear reactor fleet, and the deployment of emerging technology is assessed by simulating the system until 2100. The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for every technology, as applicable. The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}. The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018} cite IRENA.

@@

%scenario description
To explore possible pathways to curbing \gls{GHG} emissions, we simulated a total of five transition scenarios of varying likelihood, with different sets of technologies enabled for deployment, as described in Table \ref{scen-table}. The first set includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed and offshore-floating considered separately) and utility-scale lithium-ion battery storage. New deployments of oil-fuelled power plants are neglected due to the declining use of oil for electricity generation in accordance with Japan's goal of energy security and independence, as per the Basic Energy Plan. The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe),\gls{CCS}, and utility-scale hydrogen power. For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \gls{AEC}s,\gls{PEMEC}s,\gls{PEMFC}s, and \gls{SOFC}s were incoporated based on their technological potential. Along with these two technology groups, we also explore the potential impact of nuclear energy. Nuclear power has significant advantages over renewables due to its long operational lifetimes, and consequently, extremely low life-cycle emissions, and a high capacity factor. However, nuclear power faces extremely low public acceptance in Japan after the Fukushima Daiichi accident, and its future in Japan is highly uncertain. Hence, transition scenarios with and without new nuclear reactor deployment must be juxtaposed to assess the importance of the role of nuclear in emission reduction. Finally, the long-term impact of nascent hydrogen technologies on the hydrogen economy is assessed in an additional scenario. In this scenario, the potential commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored in the absence of new nuclear power.

%misc assumptions
Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively. Prices and projections for fossil fuels and nuclear fuel were incorporated \cite{wittenstein_projected_2015, world_bank_commodity_2016, international_energy_agency_world_2019}. Learning curves for costs and life-cycle emissions are compiled from existing data based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components. These learning curves are modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for a given parameter, as detailed in Table \ref{eco}. Capacity limits of renewables and \gls{PWS} are based on their land-use requirements. The maximum annual capacity growth rates for existing technologies are held constant. The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations \cite{iaea_pris_nodate}. The reactor size assumed in this study is 1165 MWe. Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow to a certain extent, which is simulated in a limited way in our model based on French reactors' range of capacity factors. The growth rates of all emerging technologies are modeled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate. One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies. We believe that these technologies, some of which are already commercialized or close to commercialization, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain. Therefore, they could be deployed as rapidly as conventional solar photovoltaic.

All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following. Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}. For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis. Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.

@@

\subsection{Sensitivity analysis}
%approach, goal, what are we hoping to learn
%variables, sampling approach, median, range, which variables, which base case scenario, why
While the aforementioned scenarios elucidate potential pathways that are likely to result in deep emission cuts, we have to acknowledge that many model parameters such as the investment cost, life cycle emissions, and lifetimes of several technologies are highly uncertain. This is especially true for nascent technologies that have not been commercialized, like \gls{CCS}, hydrogen generation and conversion technologies. Therefore our sensitivity analysis is focused on these truly unknown parameters, and their effect on the share of each of these emerging technologies in the electricity-generation mix, and on the overall system transition cost and cumulative emissions over the entire simulation time-frame.

While there is significant uncertainty in the investment cost of nuclear power plants, it varies for individual plants and not for the technology as a whole. Preliminary simulations also demonstrated that nuclear power dominates the energy mix, and its share is fairly insensitive to perturbations over known ranges of investment costs \cite{lovering_historical_2016} due to its low life cycle emissions. Furthermore, Japan has been exploring low-emission alternatives to nuclear since the Fukushima Daiichi disaster. Therefore,in order to assess all these potential alternatives which would otherwise be eliminated from the energy mix if new nuclear reactors were deployed, we chose scenario 5 (see Table \ref{scen-table}) as our base scenario for sensitivity analysis. 10 model parameters were sampled 30 times from appropriate distributions (see Table \ref{sa-vars}). The parameter value at the first year of deployment (see Table \ref{eco}) was varied, but the parameter's learning curve was held constant throughout all scenarios. For example, a 20\% change in the deployment year (2030) investment cost of \gls{SOFC}s with respect to the base case scenario reduces their investment cost in 2050 by 20\% as well.    These parameters were randomly co-varied in 30 simulations. The share of each electricity generation technology (as the ratio cumulative technology output to the cumulative electricity demand) or output of hydrogen technologies was plotted versus each varying parameter to correlate the effect of these parameters with the penetration of these technologies into the mix. A similar approach was also used to correlate these parameters with the system's transition cost, and net emissions over the entire simulation.

>>>>

\section{Methodology} \label{method}
% what is TIMES
\subsection{TIMES Model Description}
\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimization problem that is subject to a primary objective function and additional constraints \cite{loulou_etsap-tiam_2008}. The generation, refinement, supply, storage, and trade of energy commodities across multiple sectors and multiple regions are modeled using a wide variety of in-built commodity and process types. Emissions can be associated with energy commodities or processes as an emission coefficient per unit commodity produced or consumed.

@@

While electricity demand in the near future is expected to grow \cite{noauthor_electricity_2019}, long term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's aging population. However, precisely quantifying this rate of decrease is challenging as this reduction in population will likely be accompanied by increased electrification of transportation and industrial sectors. Hence, post-2030, we have assumed a conservative demand curve based on increased electrification driving increasing demand, with the demand eventually plateauing due to the aforementioned expected demographic changes. The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}. Long term impacts of factors such as the retirement of the existing nuclear reactor fleet, and the deployment of emerging technology is assessed by simulating the system until 2100. The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for every technology, as applicable. The daily and seasonal variability of renewables is incorporated using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}. The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}.

@@

%scenario description
To explore possible pathways to curbing \gls{GHG} emissions, we simulated a total of five transition scenarios of varying likelihood, with different sets of technologies enabled for deployment, as described in Table \ref{scen-table}. The first set includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed, and offshore-floating considered separately), and utility-scale lithium-ion battery storage. New deployments of oil-fuelled power plants are neglected due to the declining use of oil for electricity generation in accordance with Japan's goal of energy security and independence, as per the Basic Energy Plan. The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe), \gls{CCS}, and utility-scale hydrogen power. For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \glspl{AEC}, \glspl{PEMEC}, \glspl{PEMFC}, and \glspl{SOFC} were incoporated based on their technological potential. Along with these two technology groups, we also explore the potential impact of nuclear energy. Nuclear power has significant advantages over renewables due to its long operational lifetimes, and consequently, extremely low life-cycle emissions, and a high capacity factor. However, nuclear power faces extremely low public acceptance in Japan after the Fukushima Daiichi accident, and its future in Japan is highly uncertain. Hence, transition scenarios with and without new nuclear reactor deployment must be juxtaposed to assess the importance of the role of nuclear in emission reduction. Finally, the long-term impact of nascent hydrogen technologies on the hydrogen economy is assessed in an additional scenario. In this scenario, the potential commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored in the absence of new nuclear power.

%misc assumptions
Exogenous variables such as economic data, emission coefficients, nameplate capacity limits, and growth rates are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively. Prices and projections for fossil fuels and nuclear fuel were incorporated \cite{wittenstein_projected_2015, world_bank_commodity_2016, international_energy_agency_world_2019}. Learning curves for costs and life-cycle emissions are compiled from existing data based on expected scaling of manufacturing, availability of manufacturing materials, and the use of clean energy for manufacturing energy system components. These learning curves are modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for a given parameter, as detailed in Table \ref{eco}. Capacity limits of renewables and \gls{PWS} are based on their land-use requirements. The maximum annual capacity growth rates for existing technologies are held constant. The growth rate of nuclear power is based on historic trends and current pressure vessel manufacturing limitations \cite{iaea_pris_nodate}. The reactor size assumed in this study is 1165 MWe. Due to a projected increase in the share of renewables, nuclear power plants must be able to load follow to a certain extent, which is simulated in a limited way in our model based on French reactors' range of capacity factors. The growth rates of all emerging technologies are modeled on the rates observed for solar photovoltaic technology, with rapid initial growth followed by gradual reduction, eventually reaching a moderate maximum attainable growth rate. One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies. We assume that these technologies, some of which are already commercialized or close to commercialization, will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain. Therefore, they could be deployed as rapidly as conventional solar photovoltaic.

All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following. Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}. For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis. Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative, due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.

@@

\subsection{Sensitivity analysis}
%approach, goal, what are we hoping to learn
%variables, sampling approach, median, range, which variables, which base case scenario, why
While the aforementioned scenarios elucidate potential pathways that are likely to result in deep emission cuts, many model parameters such as the investment cost, life cycle emissions, and lifetimes of several technologies are highly uncertain. This is especially true for developing technologies like \gls{CCS}, and hydrogen generation and conversion technologies. Therefore our sensitivity analysis is focused on these truly unknown parameters, and their effect on the share of each of these emerging technologies in the electricity-generation mix, and on the overall system transition cost.

While there is significant uncertainty in the investment cost of nuclear power plants, it varies for individual plants and not for the technology as a whole. Preliminary simulations also demonstrated that nuclear power dominates the energy mix, and its share is fairly insensitive to perturbations over known ranges of investment costs \cite{lovering_historical_2016} due to its low life cycle emissions. Furthermore, Japan has been exploring low-emission alternatives to nuclear since the Fukushima Daiichi disaster. Therefore, in order to assess all these potential alternatives which would otherwise be eliminated from the energy mix if new nuclear reactors were deployed, we chose scenario 5 (see Table \ref{scen-table}) as our base scenario for sensitivity analysis. 10 model parameters were sampled 30 times from appropriate distributions (see Table \ref{sa-vars}). The parameter value at the first year of deployment (see Table \ref{eco}) was varied, but the parameter's learning curve was held constant throughout all scenarios. For example, a 20\% change in the deployment year (2030) investment cost of \gls{SOFC}s with respect to the base case scenario reduces their investment cost in 2050 by 20\% as well. This makes learning-based cost-reductions proportionate across all sensitivity analysis runs. These parameters were randomly co-varied in 30 simulations. The share of each electricity generation technology (as the ratio cumulative technology output to the cumulative electricity demand) or output of hydrogen technologies was plotted versus each varying parameter to correlate the effect of these parameters with the penetration of these technologies into the mix. A similar approach was also used to correlate these parameters with the system's transition cost.

### 2020-11-26 doc/2020-03-paper/results.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

The results of each scenario from table \ref{scen-table} are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions from each technology. Due to natural variations in renewables' output, the ability of some electricity sources to load-follow, and the increasing deployment of storage, the first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies, instead of being supplied directly to the end user. The second plot describes the transitions in terms of capacities, highlighting the effect of the capacity factor of intermittent versus base-load technologies. The third plot details the sources of direct and averaged life-cycle emissions from each source.

In Scenario 1 (Fig. \ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt. Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium-ion storage. As in all other scenarios, coal and oil must be retired by 2030. Natural gas sees rapid growth in the near-term, but complete retirement by 2055. Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards due to its load-following capabilities. All existing nuclear power plants must be restarted by 2022 at full operating capacity. With renewable energy as the only option for decarbonization, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium-ion storage are necessary. The presence of a large share of renewables results in significant overgeneration of electricity during some years. The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%). The total cost of this transition is \textbf{3,513,941 MUSD} (in 2015 USD).

With the availability of new nuclear reactors in Scenario 2 (Fig. \ref{scen2}), both 2030 and 2050 emission targets are achieved, and a further emission reduction of 12 Mt occurs by 2100. The model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear due to its low life-cycle emissions. Due to the reduction in emissions caused by nuclear power, natural gas power plants can continue to operate until 2100. The share of renewables deployed during this transition is reduced dramatically. This, combined with the load following capabilities of natural gas plants and nuclear reactors, drastically reduces the capacity of lithium-ion storage deployed. 12,220 TWh of electricity is diverted to storage, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%). The total transition cost of this scenario is the lowest, at \textbf{2,664,207 MUSD.}

Using emerging technologies without new nuclear power (Fig. \ref{scen3}), the model is able to meet both the 2030 and 2050 emission reduction goals, but no further decarbonization occurs after 2050. The results highlight the need to restart Japan's existing nuclear power plants at full capacity by 2030 in such a scenario. The deep emission cuts achieved through renewables, hydrogen, and \gls{CCS} allow the model to keep using \gls{lng} until 2100. Expansion of solar and onshore wind, along with a modest deployment of lithium-ion batteries and natural gas with \gls{CCS}, helps the model meet 2030 emission goals. After that, the model relies primarily on renewables and hydrogen to curb emissions while supplying power. Significant investment in hydrogen from 2034 onwards allows effective utilization of renewables and precludes investment in offshore floating wind power. \gls{lng}-based \gls{CCS} plays a modest role as an intermediate technology before the model can complete the transition to utility-scale hydrogen. Between 2032-2077, the model generates 2,328 TWh  of electricity from \gls{CCS} technology, which is 2\% of the electricity generated over the entire simulation time-frame. This results in 872 Mt of CO$_2$ being captured, which is well within the estimated 156 Gt CO$_2$ reservoir limit for Japan (cite Kato 2016). As the existing photovoltaic technology approaches the end of its lifetime and emerging solar technologies become cheaper and more efficient, they rapidly replace existing solar power, benefiting from the existing solar manufacture and supply chains. A total of 43,879 TWh of generated electricity is diverted to storage, primarily from solar and emerging solar technologies (48\%), fixed bottom offshore wind (28\%), and onshore wind (20\%). Much of this is used to generate 35,478 TWh worth of hydrogen, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis(99\%). The cost of this transition is \textbf{3,187,940 MUSD}.

Deploying both emerging technologies with new nuclear reactors (Fig. \ref{scen4}) results in rapid decarbonization. Both 2030 and 2050 emission targets are met, and an additional emissions reduction of 32 Mt occurs by 2100. The deployment of 50 MW nuclear obviates the need to invest in offshore wind, lithium-ion storage, and \gls{CCS}. Hydrogen plays a significant role in decarbonization, but it is deployed slightly later compared with Scenario 3, from 2037 instead. The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies(62\%), onshore wind (20\%), and nuclear (13\%). From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3. The cost of this transition is \textbf{2,804,753 MUSD}.

The fifth scenario's results (Fig. \ref{scen5}) closely resemble those of the third scenario (Fig. \ref{scen3}). However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s. Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost. Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050. The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies(48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%). From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), \gls{PEMEC} (43\%). \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%. The cost of this transition is \textbf{3,180,613 MUSD}.

\begin{figure}[htb] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nonuc}
\caption{Scenario 1 - Conventional technologies, no new nuclear.}
\label{scen1}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nuc}
\caption{Scenario 2 - Conventional technologies, with new nuclear.}
\label{scen2}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nonuc}
\caption{Scenario 3 - Emerging technologies, no new nuclear.}
\label{scen3}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nuc}
\caption{Scenario 4 - Emerging technologies, with new nuclear.}
\label{scen4}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
\label{scen5}
\end{figure}

@@

\begin{figure}[h] 
\centering
\hspace*{-3cm}
\includegraphics[scale=0.14]{figures/techs}
\caption{Sensitivity analysis of selected model parameters. Red dots indicate points that are zero values, while blue dots indicate non-zero values. Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e. PEM FC and CCS Coal). }
\label{sa-techs}
\end{figure}

\begin{figure}[h] 
\centering
\hspace*{-3cm}
\includegraphics[scale=0.14]{figures/syscost}
\caption{Sensitivity analysis of the model's overall transition cost between 2013-2100 with respect to selected model parameters.  Red dots indicate points that are zero values, while blue dots indicate non-zero values. Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e. PEM FC and CCS Coal).}
\label{sa-syscost}
\end{figure}

\begin{figure}[h] 
\centering
\hspace*{-3cm}
\includegraphics[scale=0.14]{figures/co2emi}
\caption{Sensitivity analysis of the model's cumulative emissions over 2013-2100 with respect to selected model parameters. Red dots indicate points that are zero values, while blue dots indicate non-zero values. Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e. PEM FC and CCS Coal). }
\label{sa-co2}
\end{figure}

>>>>

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
%\hspace{-3cm}
\includegraphics[scale=0.5]{figures/conv_nonuc}
\caption{Scenario 1 - Conventional technologies, no new nuclear.}
\label{scen1}
\end{figure}

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/conv_nuc}
\caption{Scenario 2 - Conventional technologies, with new nuclear.}
\label{scen2}
\end{figure}

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/newtechs_nonuc}
\caption{Scenario 3 - Emerging technologies, no new nuclear.}
\label{scen3}
\end{figure}

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/newtechs_nuc}
\caption{Scenario 4 - Emerging technologies, with new nuclear.}
\label{scen4}
\end{figure}

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/lowtrltech_nonuc}
\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
\label{scen5}
\end{figure}

The results of each scenario from table \ref{scen-table} are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions from each technology. The first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies instead of being supplied directly to the end user. The output of some technologies also varies due to their ability to load-follow. The second plot describes the transitions in terms of capacities, highlighting the effect of the capacity factor of intermittent versus base-load technologies. The third plot details the sources of direct and averaged life-cycle emissions from each source.

In Scenario 1 (Fig. \ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt. Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium-ion storage. As in all other scenarios, coal and oil must be retired by 2030. Natural gas sees rapid growth in the near-term, but complete retirement by 2055. Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards for its load-following capabilities. All existing nuclear power plants must be restarted by 2022 at full operating capacity. With renewable energy as the only option for decarbonization, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium-ion storage are necessary. The presence of a large share of renewables results in significant overgeneration of electricity during some years. The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%). The total cost of this transition is \textbf{3.51 Trillion USD} (in 2015 USD).

With the availability of new nuclear reactors in Scenario 2 (Fig. \ref{scen2}), both 2030 and 2050 emission targets are achieved, and a further emission reduction of 12 Mt occurs by 2100. The model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear due to its low life-cycle emissions. Due to the reduction in emissions caused by nuclear power, natural gas power plants can continue to operate until 2100. The share of renewables deployed during this transition is reduced dramatically. This, combined with the load following capabilities of natural gas plants and nuclear reactors, drastically reduces the capacity of lithium-ion storage deployed. 12,220 TWh of electricity is diverted to storage, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%). The total transition cost of this scenario is the lowest, at \textbf{2.66 Trillion USD.}

Using emerging technologies without new nuclear power (Fig. \ref{scen3}), the model is able to meet both the 2030 and 2050 emission reduction goals, but no further decarbonization occurs after 2050. The results highlight the need to restart Japan's existing nuclear power plants at full capacity by 2030 in such a scenario. The deep emission cuts achieved through renewables, hydrogen, and \gls{CCS} allow the model to keep using \gls{lng} until 2100. Expansion of solar and onshore wind, along with a modest deployment of lithium-ion batteries and natural gas with \gls{CCS}, helps the model meet 2030 emission goals. After that, the model relies primarily on renewables and hydrogen to curb emissions. Rapid investment in hydrogen storage from 2030 onwards allows effective utilization of renewables and precludes investment in offshore floating wind power. \gls{lng}-based \gls{CCS} plays a modest role as an intermediate technology before the model can complete the transition to utility-scale hydrogen. Between 2032-2077, the model generates 2,328 TWh  of electricity from \gls{CCS} technology, which is 2\% of the electricity generated over the entire simulation time-frame. This results in 872 Mt of CO$_2$ being captured, which is well within the estimated 156 Gt CO$_2$ reservoir limit for Japan \cite{kato_energy_2016}. As the existing photovoltaic technology approaches the end of its lifetime and emerging solar technologies become cheaper and more efficient, they rapidly replace existing solar power, benefiting from the existing solar manufacture and supply chains. A total of 43,879 TWh of generated electricity is diverted to storage, primarily from solar and emerging solar technologies (48\%), fixed bottom offshore wind (28\%), and onshore wind (20\%). Much of this is used to generate 35,478 TWh worth of hydrogen, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis (99\%) due to its greater efficiency and increasing cost-effectiveness. The cost of this transition is \textbf{3.19 Trillion USD}.

Deploying both emerging technologies with new nuclear reactors (Fig. \ref{scen4}) results in rapid decarbonization. Both 2030 and 2050 emission targets are met, and an additional emissions reduction of 32 Mt occurs by 2100. The deployment of 50 MW nuclear obviates the need to invest in offshore wind, lithium-ion storage, and \gls{CCS}. Hydrogen plays a significant role in decarbonization, but it is deployed from 2035 onwards instead of 2030, as in Scenario 3. The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies(62\%), onshore wind (20\%), and nuclear (13\%). From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3. The cost of this transition is \textbf{2.80 Trillion USD}.

The fifth scenario's results (Fig. \ref{scen5}) closely resemble those of the third scenario (Fig. \ref{scen3}). However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s, starting from 2055. Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost. Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050. The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies(48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%). From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), \gls{PEMEC} (43\%). \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%. The cost of this transition is \textbf{3.18 Trillion USD}.

@@

\begin{figure}[H] 
\centering
\hspace*{-1cm}
\includegraphics[scale=0.7]{figures/syscost_abbrv}
\caption{Sensitivity analysis for overall transition cost vs. SOFC capital costs.}
\label{syscost-smol}
\end{figure}

\begin{figure}[H] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.7]{figures/satechselc_abbrv}
\caption{Sensitivity analysis results for electricity supply shares of SOFCs and CCS Gas plants vs SOFC capital costs.}
\label{satechs-smol}
\end{figure}

Results from our sensitivity analysis are partially presented in Figures \ref{syscost-smol} and \ref{satechs-smol}, whereas the complete results are in in the appendix (Figures \ref{pws}-\ref{sa-useless}). The overall transition cost is strongly correlated with the investment cost of \gls{SOFC}s (Fig. \ref{satechs-smol}). This follows from the large share of \gls{SOFC}s, as they are the most important low-carbon technology for storing renewable power, yet they are the most expensive technology available to the model. Hence, in the absence of nuclear, they are irreplaceable, and their share is largely fixed. In analyzing the sensitivity of the output of electricity generation technologies (Fig. \ref{satechs-smol}), we unsurprisingly found the output of \gls{SOFC}s most strongly correlated with their own capital costs. However, the output of \gls{CCS} with natural gas was also most strongly correlated with the investment cost of \gls{SOFC}s, rather than the investment cost of CCS gas itself. Its share is also relatively small (indicated by the y-values in Fig. \ref{satechs-smol}), about 2-3\%.  This is because CCS gas deployment increases marginally as fuel cells deployment decreases due to increasing fuel cell cost. Therefore, the role of CCS with natural gas is that of a secondary stopgap technology that is deployed when other decarbonization alternatives are uneconomical. This is due to the large life-cycle and direct emissions of CCS gas compared to renewables and hydrogen technologies.

Remaining results indicate that \gls{PEMFC}s are never utilized due to their low efficiency compared to \gls{SOFC}s, and \gls{CCS} coal plants are never deployed due to their high emission coefficient (Fig. \ref{sa-useless}). \gls{PWS} plays a minor role in generating 0-20 TWh of hydrogen over the entire simulation's time-period (Fig. \ref{pws}), as opposed to \gls{SOEC}s which generate 19,500-22,500 TWh of hydrogen, and \gls{PEMEC}s, which generate 12,000-16,000 TWh. The share of \gls{PWS} was found to be strongly correlated with its investment cost, with \$3300/kW the approximate threshold at which this technology ceases to be cost-competitive (Fig. \ref{pws}). Its deployment is also weakly correlated with the splitting efficiency; values over 21\% seem most favourable. The emission coefficient is too small to have an impact on the overall emissions from the system considering \gls{PWS}'s small deployment, hence it does not appreciably affect its deployment. Since \gls{PEMFC}s, \gls{CCS} coal, and \gls{PWS} are not deployed in quantities significant enough to affect the model's performance, they are omitted as potential dependent variables for the rest of the sensitivity analysis.

For hydrogen generating technologies (Fig. \ref{satechs-h2}), the \gls{SOEC} output is most strongly correlated with the SOEC investment cost. However, their output is affected insignificantly by the perturbation applied to their investment cost. Their deployment is largely insensitive to their emission coefficient as their contribution to overall emissions is negligible. This highlights their vital role in the transition. \gls{PEMEC} (Fig. \ref{satechs-elc}) deployment is also most noticeably affected by their respective investment costs, but also by the investment cost of SOECs - as SOECs become more expensive, \gls{PEMEC}s emerge as the natural replacement.
